### 2019-10-11 paper/results.tex
Appendix section and table numbers fixed.Minor table fixes in methods.

\section{Results and discussion}

@@

The first mechanism adopts continuous feed flow of external thorium and $^{233}$U from \texttt{Pa-decay tank}. Hereinafter the first mechanism will be mentioned as the thorium feed mechanism. The molar fraction of the heavy metal in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. Besides, the initial fissile material fraction was increased for the five fuel salt compositions until the SD-TMS reactor was sufficiently critical at the Beginning Of Life (BOL). 
Figure~\ref{fig:keff1} illustrates the change of the effective multiplication with \gls{EFPY} for the thorium feed mechanism. As shown in Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) decreases sharply during the first 25 years of reactor operation for the first four cases. $k_{eff}$ decreases as a result of depletion of the initial fissile materials and generation of the neutron poisons (FPs). Thus, the reactor becomes subcritical within a relatively short time ($\approx$ $4$ $years$ in the \gls{TRU} case and $\approx$ $12$ $years$ in the Pu reactor-grade case). The amount of $^{233}$U generated in the \gls{SD-TMSR} is not enough to conserve the reactor criticality and overcome the neutron absorption in the initial fertile isotopes. Nevertheless, the continuous feed flow of thorium and $^{233}$U helps to operate the \gls{SD-TMSR} for a long period of time (the U-233 case). Additionally, the initial molar fraction in the LEU and Pu reactor-grade cases was increased more (see Figure~\ref{fig:keff1}) to counteract the absorption of neutrons in the non-fissile heavy metals added with the initial fuel salt. But $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.

>>>>

\section{Results and discussion} \label{Results-and-discussion}

@@

The first mechanism adopts continuous feed flow of external thorium and 
$^{233}$U from \texttt{Pa-decay tank}. Hereinafter the first mechanism will be 
mentioned as the thorium feed mechanism. The molar fraction of the heavy metal 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
Besides, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL). 
Figure~\ref{fig:keff1} illustrates the change of the effective multiplication with \gls{EFPY} for the thorium feed mechanism. As shown in Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) decreases sharply during the first 25 years of reactor operation for the first four cases. $k_{eff}$ decreases as a result of depletion of the initial fissile materials and generation of the neutron poisons (FPs). Thus, the reactor becomes subcritical within a relatively short time ($\approx$ $4$ $years$ in the \gls{TRU} case and $\approx$ $12$ $years$ in the Pu reactor-grade case). The amount of $^{233}$U generated in the \gls{SD-TMSR} is not enough to conserve the reactor criticality and overcome the neutron absorption in the initial fertile isotopes. Nevertheless, the continuous feed flow of thorium and $^{233}$U helps to operate the \gls{SD-TMSR} for a long period of time (the U-233 case). Additionally, the initial molar fraction in the LEU and Pu reactor-grade cases was increased more (see Figure~\ref{fig:keff1}) to counteract the absorption of neutrons in the non-fissile heavy metals added with the initial fuel salt. But $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.
